How to obtain the redshift distribution from probabilistic redshift estimates

### 2017-06-28 research/paper/draft.tex
now describing new mock data approach in appendix

\appendix{}

>>>>

\appendix{Catalog Production}
\label{app:catalog}

Sec. \ref{sec:mockdata} outlines one way to make mock data, but it's not 
necessarily a logically consistent way to do it, a problem identified in trying 
to use it for the test cases in Sec. \ref{sec:likelihoods}.  If the goal is to 
emulate the traditional $z_{spec}$ vs. $z_{phot}$ scatterplots, we need to 
start from probability distributions in that space.  This means there are two 
parameters $z_{spec}$ and $z_{phot}$ drawn from a two-dimensional distribution 
$p(z_{spec}, z_{phot} | \textul{\sigma}, \vec{\phi})$, where $\textul{\sigma}$ 
contains parameters concerning the relationship between $z_{spec}$ and 
$z_{phot}$, and $\vec{\phi}$ contains hyperparameters concerning $n(z)$.  We 
know from basic probability that
\begin{align}
\label{eq:trivial}
p(z_{spec}, z_{phot} | \textul{\sigma}, \vec{\phi}) =& p(z_{phot} | z_{spec}, 
\textul{\sigma}, \vec{\phi})\ p(z_{sped} | \textul{\sigma}, \vec{\phi}).
\end{align}
Because $z_{spec}$ depends only on $\vec{\phi}$ and $z_{phot}$ is independent 
of $\vec{\phi}$, this becomes
\begin{align}
\label{eq:simpler}
p(z_{spec}, z_{phot} | \textul{\sigma}, \vec{\phi}) =& p(z_{phot} | z_{spec}, 
\textul{\sigma})\ p(z_{spec} | \vec{\phi}).
\end{align}
We know how to make reasonable choices for both terms on the righthand side of 
Eq. \ref{eq:simpler}.

In the $z_{spec}$ vs. $z_{phot}$ scatterplot, $p(z_{phot} | z_{spec}, 
\textul{\sigma}, \vec{\phi})$ would be represented by vertical slices, but we 
are interested in the horizontal slices that represent $p(z_{spec} | z_{phot}, 
\textul{\sigma}, \vec{\phi})$.  Now we must distinguish the true 
hyperparameters $\vec{\phi}_{true}$ from the interim hyperparameters 
$\vec{\phi}_{int}$.  If the horizontal slices carry information about 
$\vec{\phi}$, how can we get a catalog of $p(z_{spec} | z_{phot}, 
\textul{\sigma}, \vec{\phi}_{int})$ that's consistent with $p(z_{spec} | 
z_{phot}, \textul{\sigma}, \vec{\phi}_{true})$?  Somehow that information needs 
to be propagated through in order to recover it.

We achieve this goal by dividing out the true $n(z)$ and multiplying by the 
interim $n(z)$ as in
\begin{align}
\label{eq:transformation}
p(z_{spec} | z_{phot}, \textul{\sigma}, \vec{\phi}_{int}) =& p(z_{spec} | 
z_{phot}, \textul{\sigma}, \vec{\phi}_{true})\ \frac{p(z_{spec} | 
\vec{\phi}_{int})}{p(z_{spec} | \vec{\phi}_{true}},
\end{align}
since $p(z_{spec} | z_{phot}, \textul{\sigma}, \vec{\phi})$ is separable and 
the term $p(z_{spec} | z_{phot}, \textul{\sigma})$ changes independently of the 
$p(z_{spec} | \vec{\phi})$ term.  The information about $\vec{\phi}_{true}$ is 
retained by the elements of the catalog: only $(z_{spec}, z_{phot})$ pairs 
drawn from the true distribution will be represented in the catalog!

It appears as if this is the only fully self-consistent way to ensure that a 
draw from the posterior distribution $p(z_{spec} | z_{phot}, \textul{\sigma}, 
\vec{\phi})$ does in fact follow that distribution.  In the cases with fiducial 
posteriors $p(z_{spec} | z_{phot}, \sigma, \vec{\phi})$, the method of Sec. 
\ref{sec:mockdata} was equivalent to this, but Sec. \ref{sec:likelihoods} 
requires a more sophisticated approach.
